Parks Data

### 2020-09-22 02_parks_data.Rmd
Build website

```{r fm1}
leaflet(st_buffer(parks %>% filter(grepl("Flushing Meadows", park_name)), dist = 0.000001)) %>%
  addProviderTiles(providers$Esri.WorldGrayCanvas) %>%
  addPolygons(label = ~as.character(park_name), stroke = 0.5)
```

@@

```{r fm3}
leaflet(st_transform(dissolved, 4326) ) %>%
  addProviderTiles(providers$Esri.WorldGrayCanvas) %>%
  addPolygons(stroke = 0.5,)
```

>>>>

```{r fm1, cache = FALSE}
leaflet(st_buffer(parks %>% filter(grepl("Flushing Meadows", park_name)), dist = 0.000001)) %>%
  addProviderTiles(providers$Esri.WorldGrayCanvas) %>%
  addPolygons(label = ~as.character(park_name), stroke = 0.5)
```

@@

```{r fm3, cache=FALSE}
leaflet(st_transform(dissolved, 4326) ) %>%
  addProviderTiles(providers$Esri.WorldGrayCanvas) %>%
  addPolygons(stroke = 0.5,)
```
